It is important that you correctly refer to sources. 

\begin{itemize}
\item If you describe background, according to some textbook, cite that textbook. \emph{See Example~\ref{def:consensus} below.}
\item If you make a claim about trends in industry or research, add citations to validate the claim. \emph{See Example~\ref{ex:trend} below.}
\item \textbf{Do not copy paste text from any source into your report without citation. It will be considered plagiarism.}
\item Always use the tilde character between the text and the cite command, e.g.:\begin{verbatim}
DBLP~\cite{dplg}
\end{verbatim}
The tilde inserts a space, but prevents line break between the text and citation.
\item For correct citations we recommend that you export bibtex entries from DBLP~\cite{dplg}. 
%@Hein: ACM produces crappy doi-urls for non ACM publications. I do believe that there are few papers that are part of the ACM-DL and not in DBLP.
But make sure to update the bibtex entries to adhere to the following rules.
\end{itemize}

Here are some rules to be followed for your bibliography:

\begin{itemize}
\item Make sure titles are correctly capitalized.

%You can export all nsdi citations from DBLP, accordingly this should not be a problem.
% \item Make sure abbreviations are consistent (e.g., is NSDI spelled out or
% not?) - using the @abbrev function in latex helps here.

\item Make sure there is enough info for a reader to find the document: authors
plus title isn't enough.

\item Don't blindly copy and paste ACM bibtex entries without fixing them:

- they list "New York, NY" as the address field, which means that all ACM
conferences look like they took place there; just delete this, or - better

- replace it with where the conference took place, which is much more
helpful to the reader than the publisher's address

- they have a truly weird idea about how to capitalize conference names;
just correct this (consistently)

* IEEE is equally bad, and uses a partially-inverted form of conference
names.

* Please actually review the bibliography before submitting your paper!
\end{itemize}

%@Leander: Move this to the Latex part:

And while you are at it, please:

\begin{itemize}
\item Add include{mathpmtc} in the main LaTeX file, so you don't have
math stuff in a different font than the main text. 
%We could simply add this to the template if not already done.

\item Always use the tilde character between the number and unit, e.g. 100~Mbps or 53~ms. 
The tilde inserts a space, but prevents line break between the number and unit.

\item Never put SI units in italics. 

\item Do differentiate between bits (b) and bytes (B), and between powers of 10~(MB) and 2~(MiB).

\item Avoid things like: "We refer the reader to [42]." That is, don't use citations as nouns.
\end{itemize}


\begin{example}
\label{def:consensus}
Consensus is a distributed programming abstraction that fulfills the following properties~\cite{aTextbook}:
\begin{description}
\item[Termination]
\item[Validity]
\item[Integrity]
\item[Agreement]
\end{description}
\end{example}

\noindent
\begin{example}
\label{ex:trend} Consensus systems build a fundamental part of todays cloud-computing infrastructure~\cite{spanner,chubby,zookeeper,zookeeperWeb}.
\end{example}

