Movie plots being compared in section \ref{sec:method}.
\\
Tf-idf
\begin{itemize}
    \item 1. Earth's future has been riddled by disasters, famines, and droughts. There is only one way to ensure mankind's survival: Interstellar travel. A newly discovered wormhole in the far reaches of our solar system allows a team of astronauts to go where no man has gone before, a planet that may have the right environment to sustain human life.
    \item 2. When catastrophic climate change endangers Earth's very survival, world governments unite and create the Dutch Boy Program: a world wide net of satellites, surrounding the planet, that are armed with geoengineering technologies designed to stave off the natural disasters. After successfully protecting the planet for two years, something is starting to go wrong. Two estranged brothers are tasked with solving the program's malfunction before a world wide Geostorm can engulf the planet.
    \item 3. It is the year 2029: Astronaut Leo Davidson boards a pod cruiser on a Space Station for a "routine" reconnaissance mission. But an abrupt detour through a space time wormhole lands him on a strange planet where talking apes rule over the human race. With the help of a sympathetic chimpanzee activist named Ari and a small band of human rebels, Leo leads the effort to evade the advancing Gorilla Army led by General Thade and his most trusted warrior Attar. Now the race is on to reach a sacred temple within the planet's Forbidden Zone to discover the shocking secrets of mankind's past - and the key to its future. 
    \item 7. One couple's story as they try to reclaim the life and love they once knew and pick up the pieces of a past that may be too far gone.
    \item 9. Captives of the very relationships that define and sustain them, nine women resiliently meet the travails and disappointments of life.
    \item 10. A young boy learns that he has extraordinary powers and is not of this Earth. As a young man, he journeys to discover where he came from and what he was sent here to do. But the hero in him must emerge if he is to save the world from annihilation and become the symbol of hope for all mankind.
    \item 100. After being swindled by her ex-husband, a woman takes on the Chinese legal system.
\end{itemize}

Tensorflow
\begin{itemize}
    \item 1. Earth's future has been riddled by disasters, famines, and droughts. There is only one way to ensure mankind's survival: Interstellar travel. A newly discovered wormhole in the far reaches of our solar system allows a team of astronauts to go where no man has gone before, a planet that may have the right environment to sustain human life.
    \item 2. When catastrophic climate change endangers Earth's very survival, world governments unite and create the Dutch Boy Program: a world wide net of satellites, surrounding the planet, that are armed with geoengineering technologies designed to stave off the natural disasters. After successfully protecting the planet for two years, something is starting to go wrong. Two estranged brothers are tasked with solving the program's malfunction before a world wide Geostorm can engulf the planet.
    \item 3. Six astronauts aboard the space station study a sample collected from Mars that could provide evidence for extraterrestrial life on the Red Planet. The crew determines that the sample contains a large, single-celled organism - the first example of life beyond Earth. But..things aren't always what they seem. As the crew begins to conduct research, and their methods end up having unintended consequences, the life form proves more intelligent than anyone ever expected.
    \item 7. One of the few remaining drone repairmen assigned to Earth, its surface devastated after decades of war with the alien Scavs, discovers a crashed spacecraft with contents that bring into question everything he believed about the war, and may even put the fate of mankind in his hands.
    \item 9. Is it humankind's greatest achievement? 12 billion miles away a tiny spaceship is leaving our Solar System and entering the void of deep space. It is the first human-made object ever to do so. Slowly dying within its heart is a plutonium generator that will beat for perhaps another decade before the lights on Voyager finally go out. But this little craft will travel on for millions of years, carrying a Golden Record bearing recordings and images of life on Earth. In all likelihood Voyager will outlive humanity and all our creations. It could be the only thing to mark our existence. Perhaps some day an alien will find it and wonder. The story of Voyager is an epic of human achievement, personal drama and almost miraculous success. Launched 16 days apart in Autumn 1977, the twin Voyager space probes have defied all the odds, survived countless near misses and almost 40 years later continue to beam revolutionary information across unimaginable distances. With less computing power than a modern hearing aid, they have unlocked the stunning secrets of our Solar System on a journey as revolutionary as the first circumnavigation of the globe and humankind's first footprint on the moon. In this powerful, poetic and cinematic feature documentary, THE FARTHEST celebrates these magnificent machines, the men and women who built them and the vision that propelled them farther than anyone could ever have hoped. Launched from a fractious planet, these pioneers sail on serenely in the darkness - an enduring testament to the ingenuity of humankind and the untapped limits of the human imagination. Passionate organic storytelling with people, images, archive and opinion woven with daring and brio makes THE FARTHEST a genuinely cinema-scale adventure.
    \item 10. Europa, Jupiter's moon is known to have potential to support life. Hence a manned mission is sent to Europa to search for data proving existence of life there. "Europa report" shows the difficult choices and sacrifices the crew has to make to fulfill their objective of sending valuable data to Earth for research.
    \item 100. Originally a 30 minute portion for an anthology film, Impostor was retooled into a full length feature film. Based on the Philip K. Dick short story of the same name, it follows the lead character Spencer Olham's quest to regain his identity after being suspected as an alien android, in an future Earth at war with aliens that use the androids as bombs to destroy their enemies homeworlds.
\end{itemize}